---
title: "Corona Virus Report"
author:
- familyname: Tsakis
  othernames: Alexi
  address: Monash Universtidy
  email: atsa0003@student.monash.edu
  correspondingauthor: true
  qualifications:  XXX
- familyname: XXXX
  othernames: Reports
  address: XXX
  qualifications: XXX
- familyname: XXX
  othernames: XXX
  address: XXX
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries
library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
```

\section*{Country XX1 and YY1"}

\section*{Country XX2 and YY2}

\section*{Country Myanmar and Guernsey}

```{r}
library(lubridate)
options(scipen=10)
set.seed(96024)
data = read.csv("data/worldwidecases.csv")
sample(unique(data$countriesAndTerritories),2)

data_mg = data %>%
  filter(countriesAndTerritories %in% c("Myanmar","Guernsey")) %>%
  mutate(day_of_year = yday(as.Date(dateRep,format='%d/%m/%Y'))) %>%
  mutate(pct_pop = (cases/popData2018)*100)

data_mg %>%
  ggplot(aes(x=day_of_year,y=cases,col=countriesAndTerritories))+geom_line()

data_mg %>%
  ggplot(aes(x=day_of_year,y=pct_pop,col=countriesAndTerritories))+geom_line()

data %>%
  filter(continentExp %in% c("Europe","Asia")) %>%
  mutate(pct_pop = (cases/popData2018)*100) %>%
  mutate(day_of_year = yday(as.Date(dateRep,format='%d/%m/%Y'))) %>%
  group_by(continentExp,month) %>%
  summarise(mean=mean(pct_pop))

data_mg %>%
  group_by(countriesAndTerritories,month) %>%
  summarise(mean=mean(pct_pop))
```
For this section we will discuss the impact of coronavirus in Guernsey and Myanmar.

- Guernsey is one of the channel islands in the English Channel near the French coast. It has a total area of 65 square kilometres, is accessible only by sea, and has a population of approximately 60,000.
- Myanmar is a country in Southeast Asia, bordered by Bangladesh, India, China, Laos and Thailand land-wise, as well as the Andaman Sea and the Bay of Bengal. It has a population of approximately 54 million.

Using the data we have, we have compared the impact of coronavirus on the two relative to their respective continents, their population size and raw numbers based on the cases they have.

- Guernsey was not hit hard by coronavirus in terms of absolute number of cases (see graph 1 and 2), however in terms of percentage of population relative to the average for the rest of Europe, coronavirus had a large impact - approximately double the percentage of population affected in month 3 and 4 (See table 1 and 2).
- Myanmar was not affected by coronavirus, having only approximately the same number of total cases as Guernsey for its much larger population (see graph 1 and 2), and compared to the rest of Asia's average percentage of population affected, it is much lower (See table 1 and 2).
